\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr} 
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\large Moana Stadelmann} \\ 
    \vspace{2mm}
    moana.stadelmann@uzh.ch \space\space\space|\space\space\space
    \href{https://github.com/MoanaStadelmann}{GitHub} \space\space\space|\space\space\space
    \href{https://www.linkedin.com/in/moanastadelmann}{LinkedIn}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Intern in Data Analytics}{July 2025 -- September 2025}
    {Statistik Aargau -- Department of Finance and Resources}{Aargau, CH}
    \resumeItemListStart
      \resumeItem{Refined and developed approaches for the systematic and automated plausibility checks of election results; contributed to optimizing the filing of statistics from the Structural Survey; supported the decluttering of the archive.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {Research Assistant}{September 2024 -- September 2025}
    {ETH Zurich -- Public Policy Group}{Zurich, CH}
    \resumeItemListStart
      \resumeItem{Project: Which strategies are effective for countering online hate speech?}
      \resumeItem{Responsibilities: supported the development of the data pipeline.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {Business Analyst}{April 2023 -- February 2025}
    {Nosco Analysis AG}{Zurich, CH}
    \resumeItemListStart
      \resumeItem{Fintech start-up providing digitalisation solutions for Swiss pension funds and their partners in performance and risk management.}
      \resumeItem{Responsibilities: data collection and harmonisation, product development.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {Research Assistant}{March 2023 -- May 2023}
    {University of St. Gallen -- Chair of Comparative Political Behavior}{St. Gallen, CH}
    \resumeItemListStart
      \resumeItem{Project: Internet ownership and control in authoritarian contexts.}
      \resumeItem{Responsibilities: data collection, correction, and quality control.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Master of Science in Data Science (Minor in Economics)}{2023 -- Present}
    {University of Zurich}{Zurich, CH}
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Arts in Economics}{2019 -- 2023}
    {University of St. Gallen}{St. Gallen, CH}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Bachelor’s thesis}: Analyzed the impact of the introduction of paternity leave in Switzerland on fathers’ employment using a \textit{Difference-in-Differences} (DiD) identification strategy and the \textit{Swiss Labour Force Survey} (SLFS).
    }}
  \end{itemize}
\resumeSubHeadingListEnd

%-----------ADDITIONAL QUALIFICATIONS-----------
\section{Additional Qualifications}
\resumeSubHeadingListStart
  \resumeSubheading
    {Certificate in Data Science Fundamentals (DSF)}{2021 -- 2023}
    {University of St. Gallen}{}
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {Specialization in Data Analytics and Data Handling}{2019 -- 2023}
    {University of St. Gallen}{}
\resumeSubHeadingListEnd

%-----------LANGUAGES & SKILLS-----------
\section{Languages and Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming languages}: R, Python, SQL, Java, TypeScript, C \\
    \textbf{Languages}: German (native), English (C2), French (B2)
  }}
\end{itemize}

%-----------EXTRACURRICULAR-----------
\section{Extracurricular Activities}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Foodsavemarkt}: Preparing vegetables left over by suppliers for major distributors to reduce food waste. \\
    \textbf{Board Member, Student Impact}: Community engagement, planning and management of events.
  }}
\end{itemize}

\end{document}
